---
title: "CODE_BOOK"
author: "Danilo Ac Herrera"
date: "27/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Getting and Cleaning Data Course Project

The run_script explanation variables:

variables and explanation 
"features" contains information from "UCI HAR Dataset/features.txt" file.
"activities" contains information from "UCI HAR Dataset/activity_labels.txt"
"subject_test" contains information from "UCI HAR Dataset/test/subject_test.txt"
"x_test" contains information from "UCI HAR Dataset/test/X_test.txt"
"y_test" contains information from "UCI HAR Dataset/test/y_test.txt"
"subject_train" contains information from "UCI HAR Dataset/train/subject_train.txt"
"x_train" contains information from "UCI HAR Dataset/train/X_train.txt"
"y_train" contains information from "UCI HAR Dataset/train/y_train.txt"
"subject" contains the join rows from subject_test and subject_train
"x" contains the join rows from x_test and x_train
"y" contains the join rows from y_test and y_train
"mdata" contains the bind columns of the subject, x, y
"tdata" contains the selected columns "subject" and those who contains "mean" and "std" values in names
"independent" contains the result data frame of grouping and summarize "tdata"


```{r independent}
View(independent)
```
